On the properties of discs around accreting brown dwarfs

### 2010-05-19 BD_disc/paper.tex
removed some files that shouldn't be in cvs - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2273 25464f21-6099-402c-b30a-640f1d40d38b

There are also risks of observational biases at the low-mass end of
the correlation. Radiative-transfer modelling of H$\alpha$ emission
from accreting BDs requires high temperatures ($>$\, 10\,kK) in the
accretion funnels in order to recover the level of emission that is
observed. (Cooling rate arguments can be invoked to explain the
presence of such high temperatures). Recently some continuum
measurements of accreting BDs have been conducted, and these broadly
support the H$\alpha$ rates
\citep{muzerolle_2003,natta_2004,natta_2006}. Nonetheless
it is worth considering the observed effect that mass accretion at
typical CTTS rates onto a BD might have. Parity between the BD
photospheric luminosity and the accretion luminosity occurs at
relatively low accretion rates \citep{clarke_2006}. Such
objects may not be detected as BDs at all in photometric surveys. Even
before such an extreme case is reached, the additional luminosity
provided by the accretion should have measurable effect on the BD
colours. Furthermore the additional flux will be reprocessed by the
disc, altering its scaleheight and possibly the shape of its inner
edge.

@@

XXXX TJH check this now

Accretion rates derived for pre-MS stars are of order \logmdot = $-6$
to $-11$ \citep{natta_2006}.  With the largest accretion
rates found in so-called FU Orionis type objects (after the object
where they were first observed). For the more typical accretion rates
\citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9} M_{\odot}yr^{-1}$, for
  TTS,][]{dahm_2009}, several studies have now suggested
that the accretion rate is strongly correlated with the mass of the
central star. This relationship was perhaps first suggested by
\cite{muzerolle_2003} using various accretion diagnostics. Later,
\citep{muzerolle_2005} derived a relationship of approximately
$\dot{M}\propto M_*^{~2}$. Further evidence was put forward by
\cite{natta_2004}, where accretion rates as low as 5$\times$
10$^{-12}M_{\odot} yr^{-1}$ were found for BD stars. More recently,
even lower accretion rates of $\approx$10$^{-13}M_{\odot} yr^{-1}$,
have been derived for BDs by \cite{herczeg_2009}.  Further
support for a dependence of accretion rate on stellar mass was
apparent in the significantly more homogeneous dataset of
\cite{natta_2006}. \cite{natta_2006} analysed a set
of accretion rates and masses derived for pre-MS stars in $\rho$
Ophiuchi and compared these results to stars in Taurus. They found
that the accretion rate scales with central object mass, into the BD
regime.

For any $\dot{M}\propto M_*$ relationship to be ratified, clearly, the
associated mass derivations must be shown to be accurate. For the BD
mass regime it has been demonstrated that classification, either
spectroscopic or photometric, and therefore accurate mass derivation
is exceedingly difficult for BDD systems
\citep{walker_2004}. The inclusion of significant levels of
accretion flux will act to exacerbate this problem. Essentially, as BD
mass objects have relatively cool photospheres, compared to the
temperature of the accretion hotspots, meaning that for lower
accretion rates, than for their CTTS counterparsts, the accretion flux
dominates the small wavelength regime of the SED.

Therefore, to strengthen, or reject, any stellar mass to accretion
rate relationship, the limits of observational classification (and
mass derivation) of accreting BDD systems must be understood. To
provide a benchmark model grid of such systems, with which to aid
interpretation of the observational data, we must select a range of
accretion rates including and exceeding those detected for systems
previously classified as BDs.

@@

\begin{table*}
\begin{tabular}{|l|l|}
Input parameter&Values (\# values)\\
\hline
Mass ($M_{\odot}$)&0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 (8)\\
Age (Myr)&1 \& 10 (2)\\
Rotation period (days)&0.5 \& 5 (2)\\
Areal coverage (of $\dot{M}$, \%)&1 \& 10 (2)\\
Accretion rate (log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$)&$-6$, $-7$, $-8$, $-9$, $-10$,
$-11$ \& $-12$ (7)\\
Disc mass ($M_*$)&0.01 (1)\\
Inclination ($^{\circ}$)&0, 27, 39, 48, 56, 64, 71, 77, 84 \& 90
(10)\\
\end{tabular}
\caption{List of all varied input parameters. Resulting in a total
  number of models of 448 (plus 40 models without radiative transfer
  simulations for the naked BDs) and 4480 SEDs (plus 40 for naked
  BDs). \label{par_space_table}}
\end{table*}

@@

@@

As discussed in \cite{walker_2004} discs around CTTS stars
have scaleheights at 100 AU of between $h$(100)$=$7 to 20 AU, whereas
for BDD systems, $h$(100)=20 to 60 AU (for 0.08 and 0.01 $M_{\odot}$
respectively). Our models adopt the same formalism for solving
hydrostatic equilibrium and therefore, at negligible accretion rates,
our disc scaleheights are comparable. As the accretion rate increases
the flux levels of the central star increase and lead to heating of
the disc which in turn leads to vertical expansion. For
our models we found that levels of vertical flaring increased
marginally with accretion rate. Significant differences, more than
$>$5 AU increase in $h(50)$, in the vertical structure were not
apparent until the high accretion rates of \logmdot = $-7$ and
$-6$. Figures \ref{flare_-12_183} and \ref{flare_-7_193} show the
density structure ($log({\rho})$) in the disc from radial distances of
0 to 50 AU for example systems ($M_*=0.04M_{\odot}$, Age=1 Myrs,
$\tau$=5 and areal coverage=10\%), with accretion rates of \logmdot =
$-12$ and $-7$, respectively.

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/flare_-12_183.ps"
   hoffset=10 voffset=-40 hscale=33 vscale=33 angle=0}
 \caption{Figure showing the density structure ($log({\rho}$)) of the
   BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
   coverage=10\% and accretion rate of \logmdot=$-12$.
   \label{flare_-12_183}}
\end{figure}

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/flare_-7_193.ps"
  hoffset=10 voffset=-40 hscale=33 vscale=33 angle=0}
\caption{Figure showing the density structure ($log({\rho}$)) of the
  BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
  coverage=10\% and accretion rate of \logmdot=$-7$.
   \label{flare_-7_193}}
\end{figure}

Figure \ref{flare_-12_183} shows that for a typical BDD system the
resulting disc is highly flared and therefore, the opening angle for
stellar radiation is small. As discussed the flaring for BDD systems
was found to be larger than CTTS systems by
\cite{walker_2004}. \cite{walker_2004}, state that the
degree of disc flaring depends on the disc temperature structure and
the mass of the central star, with the disc scaleheight $h\propto
\frac{T_{\rm disc}}{M_*}^{1/2}$ \citep{shakura_1973}. Recently,
\cite{ercolano_2009} suggest the inverse relation of flaring
with stellar mass, i.e. $h\propto M_*$. This suggestion was based on
evidence from \cite{allers_2006}, where SEDs for 17 systems in
the mass range 6$M_{\rm Jup}<M_*<$350$M_{\rm Jup}$ were fit with
flared or flat disc models. In general, \cite{allers_2006}
find that lower mass objects achieve better fits with the flat disc
models and higher mass objects with the flared discs.

@@

A quick comparison of Figures \ref{flare_-12_183} and
\ref{flare_-7_193} show an increase in the scaleheight at 50 AU of
$>$5 AU, as the accretion rate moves from \logmdot =$-12$ to
$-7$. However, despite this small change with high levels of accretion
our grid shows scaleheights comparable to the work of
\cite{walker_2004} and as such result in similar consequences
for the SEDs and photometric magnitudes. The effects of this flaring
and the increase in flaring for very high accretion levels on SEDs and
photometric magnitudes are discussed in Sections \ref{sed_analysis}
and \ref{photometry}, respectively.

\subsubsection{Inner edge}
\label{inner_edge}

Our models include a sophisticated treatment of dust sublimation
(described in Section \ref{dust_edge}). In contrast to the models of
\cite{walker_2004}, who apply a dust destruction radius, we
set the initial inner radius of the disc at the co-rotation radius of
the system. However, as our models then sublimate dust during the
temperature convergence routine this inner edge location may change.
As the flux levels of the central star increase with increasing
accretion rates the flux incident on the inner edge increases and
leads to increasing erosion of the inner edge of the dust disc.

As the inner edge moves its temperature is expected to change, this
has been predicted to lead to a correlation of inner edge position and
IR excess \citep{meyer_1997}. This may act to bias surveys
correlating rotation rates with IR excess to search for evidence of
disc-locking. However, the flux from the inner edge will usually peak
between 2 and 3\,$\mu$m \citep{dullemond_2001}, given that the dust
sublimation temperature peaks at $\approx$1400\,K for canonical
densities. This means that for models where dust is sublimated the
inner edge will have maximum temperatures of $\approx$1400\,K and this
correlation of disc position and temperature will be lost.

@@

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/lum_sub.ps"
   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
 \caption{Figure showing the combined stellar luminosity (accretion
   plus intrinsic stellar luminosity) in units of
   log($L_*/L_{\odot}$) against the change in inner edge location
   shown in units of AU (\textit{top panel}) and $R_*$ (\textit{bottom
     panel}).
   \label{lum_sub}}
\end{figure}

The \textit{top panel} of Figure \ref{lum_sub} shows that as the
luminosity increases the total change in the inner radius increases as
more of the disc is sublimated. The total change for lower
luminosities at lower than $~$0.2 log($L_*/L_{\odot}$) is small (less
than $~$0.02 AU). As the luminosities increases to larger, and extreme
values, due to increasing accretion, the dust sublimation
increases. In the \textit{bottom panel} the change in inner radius
tends towards around $~$120 $R_*$. Increases in accretion rate, for
extreme accretors, dominates the increase in stellar luminosity. As
pre-MS stars age they contract. Therefore, for lower accretion rates,
younger, and therefore larger stars will have greater luminosities
than the equivalent older stars. Therefore, the major contributors to
the X-axis of Figure \ref{lum_sub} are controlled by the input
parameters of accretion rate and age. The initial inner wall radius
was set as the magnetic co-rotation radius (see Section
\ref{physics}). This distance is a strong function of rotational
period, with $R_{\rm inner}\propto \tau^{2/3}$ (see Equation
\ref{inner_eq}) which is in turn a function of stellar radius. The
stellar radius itself is then a function of the stellar
age. Therefore, the initial inner wall edge position will change as a
function of the input variables of rotational period and age. The
initial position of the inner edge will control the amount of the
stellar flux intercepted by the inner edge wall. Therefore the amount
that the disc will be sublimated will also be a function of the
initial position of the inner edge.

Figure \ref{delta_radius} shows the initial inner edge position, or
the co-rotation radius ($R_*$) against the change in inner edge
location ( $R_{\rm inner}-R_{\rm co}$, $R_*$). The \textit{panels} of
Figure \ref{delta_radius} then shows these data for two accretion
levels and at the two ages and rotation periods. These input variables
for our model grid are the underlying variables controlling, as
discussed, the dust sublimation process. The \textit{top panels} are
for models with accretion rates of -9, -10, -11 and -12
log$(\frac{\dot{M}}{M_{\odot}}yr{-1})$, classed as typical accretors
here and throughout the rest of this work. The typical accretors are
then separated further into three groups in the \textit{top left
  panel} specifically, -9, -10 and -11 \& -12
log$(\frac{\dot{M}}{M_{\odot}}yr^{-1})$ (blue, red and black dots
respectively). The \textit{bottom panels} show the data for models
with accretion rates of \logmdot = $-6$, $-7$ and $-8$ (blue, red and
black dots respectively), which we have classed as extreme
accretors. The \textit{right panels} show the data separated by age,
with 1 and 10 Myrs (as crosses and triangles respectively), and
rotation period, with 0.5 and 5 days (as red and blue symbols
respectively).

\begin{figure}
  \vspace*{174pt}
  \special{psfile="Fig/delta_radius.ps"
   hoffset=235 voffset=0 hscale=30 vscale=30 angle=90}
 \caption{Figure showing data for the co-rotation radius ($R_{\rm
     co}$) against the change in inner edge location ( $R_{\rm
     inner}-R_{\rm co}$) both in units of $R_*$. The typical accretors
   are shown in the \textit{top panels} and the extreme accretors in
   the \textit{bottom panels} (see text for explanation). The
   accretion rates are then further subdivided. The \textit{top left
     panel} shows accretion rates of \logmdot = $-9$, $-10$, $-11$
   \& $-12$ as blue, red and black dots
   respectively. In the \textit{bottom left panel} accretion rates of
   \logmdot = $-6$, $-7$ and $-8$ are shown as
   blue, red, and black dots. In addition the \textit{left panels}
   separates the systems by age and period. The systems with ages of 1
   and 10 Myrs are shown as crosses and triangles respectively. The
   systems with rotation rates of 0.5 and 5 days are then shown as red
   or blue symbols respectively. \label{delta_radius}}
\end{figure}

@@

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/no_sub_183_density.ps}\label{no_sub_183_a}}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/no_sub_183_temp.ps}\label{no_sub_183_b}}
  \caption{Figure showing final density (log($\rho$)) where dust is
    present (colour scale) as the \textit{left panel} and temperature,
    \textit{right panel}, for a system with no dust
    sublimation. System parameters are: $M_*$=0.04$M_{\odot}$, Age=1
    Myrs and areal coverage=10\%, $\tau$=5 days and accretion rate \logmdot$=-12$.}
  \label{no_sub_183}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_169_density.ps}\label{sub_169_a}}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_169_temp.ps}\label{sub_169_b}}
  \caption{Figure showing both the initial (grey scale) and final
    density (log($\rho$)) where dust is present (colour scale) as the
    \textit{left panel} and temperature, \textit{right panel}, for a
    system with no dust sublimation. System parameters are:
    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
    $\tau$=0.5 days and accretion rate \logmdot=$-12$.}
  \label{sub_169}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_175_density.ps}\label{sub_175_a}}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_175_temp.ps}\label{sub_175_b}}
  \caption{Figure showing both the initial (grey scale) and final
    density (log($\rho$)) where dust is present (colour scale) as the
    \textit{left panel} and temperature, \textit{right panel}, for a
    system with no dust sublimation. System parameters are:
    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
    $\tau$=0.5 days and accretion rate \logmdot$=-9$.}
  \label{sub_175}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_179_density.ps}\label{sub_179_a}}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_179_temp.ps}\label{sub_179_b}}
  \caption{Figure showing both the initial (grey scale) and final
    density (log($\rho$)) where dust is present (colour scale) as the
    \textit{left panel} and temperature, \textit{right panel}, for a
    system with no dust sublimation. System parameters are:
    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
    $\tau$=0.5 days and accretion rate \logmdot$=-7$.}
  \label{sub_179}
\end{figure*}

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_181_density.ps}\label{sub_181_a}}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/sub_181_temp.ps}\label{sub_181_b}}
  \caption{Figure showing both the initial (grey scale) and final
    density (log($\rho$)) where dust is present (colour scale) as the
    \textit{left panel} and temperature, \textit{right panel}, for a
    system with no dust sublimation. System parameters are:
    $M_*$=0.04$M_{\odot}$, Age=1 Myrs and areal coverage=10\%,
    $\tau$=0.5 days and accretion rate \logmdot$=-6$.}
  \label{sub_181}
\end{figure*}

>>>>

There are also risks of observational biases at the low-mass end of
the correlation. Radiative-transfer modelling of H$\alpha$ emission
from accreting BDs requires high temperatures ($>$\, 10\,kK) in the
accretion funnels in order to recover the level of emission that is
observed \citep{muzerolle_2003,natta_2004,natta_2006}. (Cooling rate
arguments can be invoked to explain the presence of such high
temperatures). Recently some continuum measurements of accreting BDs
have been conducted \cite{herczeg_2009}, and these broadly support the H$\alpha$
rates.

Nonetheless it is worth considering the observed effect that mass
accretion at typical CTTS rates onto a BD might have. Parity between
the BD photospheric luminosity and the accretion luminosity occurs at
relatively low accretion rates \citep{clarke_2006}: Such objects may
not be detected as BDs at all in photometric surveys. Even before such
an extreme case is reached, the additional luminosity provided by the
accretion should have measurable effect on the BD colours. Furthermore
the additional flux will be reprocessed by the disc, altering its
scaleheight and possibly the shape of its inner edge.

@@

Accretion rates derived for pre-MS stars are of order \logmdot = $-6$
to $-11$ \citep{natta_2006}, with the largest accretion rates found in
so-called FU Orionis type objects. For the more typical accretion
rates \citep[$\dot{M}=$10$^{-11}$ to 10$^{-8.9} M_{\odot}yr^{-1}$, for
  TTS,][]{dahm_2009}, several studies have now suggested that the
accretion rate is strongly correlated with the mass of the central
star. This relationship was perhaps first suggested by
\cite{muzerolle_2003} using various accretion diagnostics. Later,
\citep{muzerolle_2005} derived a relationship of approximately
$\dot{M}\propto M_*^{~2}$. Further evidence was put forward by
\cite{natta_2004}, where accretion rates as low as 5$\times$
10$^{-12}M_{\odot} yr^{-1}$ were found for BD stars. More recently,
even lower accretion rates of $\approx$10$^{-13}M_{\odot} yr^{-1}$,
have been derived for BDs by \cite{herczeg_2009}.  Further support for
a dependence of accretion rate on stellar mass was apparent in the
significantly more homogeneous dataset of
\cite{natta_2006}. \cite{natta_2006} analysed a set of accretion rates
and masses derived for pre-MS stars in $\rho$ Ophiuchi and compared
these results to stars in Taurus. They found that the accretion rate
scales with central object mass into the BD regime, although with
significant scatter.

@@

\begin{table*}
\begin{tabular}{|l|l|}
Input parameter&Values (\# values)\\
\hline
Mass ($M_{\odot}$)&0.01, 0.02, 0.03, 0.04, 0.05, 0.06, 0.07 \& 0.08 (8)\\
Age (Myr)&1 \& 10 (2)\\
Rotation period (days)&0.5 \& 5 (2)\\
Areal coverage (of $\dot{M}$, \%)&1 \& 10 (2)\\
Accretion rate (log$(\frac{\dot{M}}{M_{\odot}} yr^{-1})$)&$-6$, $-7$, $-8$, $-9$, $-10$,
$-11$ \& $-12$ (7)\\
Disc mass ($M_*$)&0.01 (1)\\
Surface density profile & $r^{-1}$ (1) \\
Inclination ($^{\circ}$)&0, 27, 39, 48, 56, 64, 71, 77, 84 \& 90
(10)\\
\end{tabular}
\caption{List of all varied input parameters. Resulting in a total
  number of models of 448 (plus 40 models without radiative transfer
  simulations for the naked BDs) and 4480 SEDs (plus 40 for naked
  BDs). \label{par_space_table}}
\end{table*}

@@

XXXX Nathan - add disc structure equation here and remove walker references.

@@

We have previously tested the {\sc torus} code against that used by
Walker and co-workers, using a CTTS disc model and simultaneously
solving for radiative and hydrostatic equilibrium (but not employing
dust sublimation). These tests showed excellent agreement in density
and temperature structure (as well as in the resultant SEDs). The
results of these tests were presented by \cite{walker_2006}. It is
therefore unsurprising that at negligible mass-accretion rates our
disc structures are very similar to those present in
\cite{walker_2004}. Typical discs around CTTS stars have scaleheights
at 100\,AU of between $h$(100)$=$10 to 20\,AU, whereas for BDD
systems, $h$(100)=20 to 60\,AU (for 0.08 and 0.01 $M_{\odot}$
respectively). As the accretion rate increases the flux levels of the
central star increase and lead to heating of the disc which in turn
leads to vertical expansion. We found that levels of vertical flaring
increased only marginally with accretion rate. Significant
differences, more than $>$5\,AU increase in $h(50)$, in the vertical
structure were not apparent until the high accretion rates of \logmdot
= $-7$ and $-6$. Figures \ref{flare_-12_183} and \ref{flare_-7_193}
show the density structure ($\log \rho$) in the disc from radial
distances of 0 to 50\,AU for example systems ($M_*=0.04M_{\odot}$,
Age=1\,Myrs, $\tau$=5\,d and areal coverage=10\%), with accretion
rates of \logmdot = $-12$ and $-7$, respectively.

\begin{figure*}
\begin{center}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-12_183.ps}\label{flare_-12_183}}
  \subfigure[]{\includegraphics[scale=0.4,angle=0]{./Fig/flare_-7_193.ps}\label{flare_-7_193}}
\end{center}
 \caption{Figure showing the density structure ($\log \rho$) of the
   BDD system with $M_*=0.04M_{\odot}$, Age=1 Myrs, $\tau$=5, areal
   coverage=10\% and accretion rate of (a) \logmdot=$-12$ and (b) \logmdot = $-7$.}
\end{figure*}

\cite{walker_2004} state that the degree of disc flaring depends on
the disc temperature structure and the mass of the central star, with
the disc scaleheight $h\propto \frac{T_{\rm disc}}{M_*}^{1/2}$
\citep{shakura_1973}. Recently however \cite{ercolano_2009} proposed
the inverse relation of flaring with stellar mass, i.e. $h\propto
M_*$. This suggestion was based on evidence from \cite{allers_2006},
where SEDs for 17 systems in the mass range 6$M_{\rm
  Jup}<M_*<$350$M_{\rm Jup}$ were fit with flared or flat disc
models. In general, \cite{allers_2006} find that lower mass objects
achieve better fits with the flat disc models and higher mass objects
with the flared discs.

@@

A  comparison of Figures \ref{flare_-12_183} and
\ref{flare_-7_193} shows an increase in the scaleheight at 50\,AU of
$>$5 AU, as the accretion rate moves from \logmdot =$-12$ to
$-7$. However, despite this small change with high levels of accretion
our grid shows scaleheights comparable to the work of
\cite{walker_2004} and as such result in similar consequences for the
SEDs and photometric magnitudes. The effects of this flaring and the
increase in flaring for very high accretion levels on SEDs and
photometric magnitudes are discussed in Sections \ref{sed_analysis}
and \ref{photometry}, respectively.

\subsubsection{Inner edge of the dust disc}
\label{inner_edge}

The inner edge of the gas disc is fixed at the co-rotation radius, at
which point the gas threads onto the magnetic field and follows the
field lines in a funnel flow towards the protostellar surface. We make
the assumption that the dust (should it exist at the co-rotation
radius) is destroyed in the funnel flows. This is a reasonable
assumption from both theoretical and observational perspectives:
Radiative-transfer models indicate the temperature in the funnel flows
may be very much greater than the dust sublimation temperature
($>10$\,kK, \citep{muzerolle_2003}), while dusty funnel flows are
likely to be optically thick in the visible, which would lead to
substantial photometric variability as the funnels transit the
photosphere--an effect that is unobserved.

Our models include a sophisticated treatment of dust sublimation
(described in Section \ref{dust_edge}).  As the flux levels of the
central protostar increase with increasing accretion rates the flux
incident on the inner edge increases and leads to increasing erosion
of the inner edge of the dust disc.

As the inner edge moves its temperature is expected to change, this
has been predicted to lead to a correlation of inner edge position and
IR excess \citep{meyer_1997}. This may act to bias surveys correlating
rotation rates with IR excess to search for evidence of
disc-locking. However, the flux from the inner edge will usually peak
between 2 and 3\,$\mu$m \citep{dullemond_2001}, given that the dust
sublimation temperature peaks at $\approx$1400\,K for canonical
densities. This means that for models where dust is significantly
sublimated the inner edge will {\em always} have a temperature of
$\approx$1400\,K and this correlation of disc position and temperature
will be lost.

@@

@@

\begin{figure*}
  \centering
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/no_sub_183_density.ps}\label{no_sub_183_a}}
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/no_sub_183_temp.ps}\label{no_sub_183_b}}
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_179_density.ps}\label{sub_179_a}}
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_179_temp.ps}\label{sub_179_b}}
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_181_density.ps}\label{sub_181_a}}
  \subfigure[]{\includegraphics[scale=0.33,angle=0]{./Fig/sub_181_temp.ps}\label{sub_181_b}}

  \caption{Figure showing both the initial (grey scale) final density
    ($\log \rho$) where dust is present (colour scale, left-hand
    panels) and temperature (right-hand panels). System parameters
    are: $M_*$=0.04$\,M_{\odot}$, Age=1\,Myrs and areal coverage=10\%,
    $\tau$=5\,days and accretion rate \logmdot$=-12$ (a, b);
    $M_*$=0.04$M_{\odot}$, Age=1\,Myrs and areal coverage=10\%,
    $\tau$=0.5\,days and accretion rate \logmdot$=-7$ (c, d);
    $M_*$=0.04$M_{\odot}$, Age=1\,Myrs and areal coverage=10\%,
    $\tau$=0.5\,days and accretion rate \logmdot$=-6$ (e, f).}
\end{figure*}
